%-------------------------
% Resume in Latex
% Author : Matty
% Based on: https://github.com/jakegut/resume (which was itself based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{geometry}
\usepackage{ragged2e}


\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% margins
\geometry{
    letterpaper,
    top=1in,       % Adjust as needed
    bottom=1in,    % Adjust as needed
    left=0.75in,   % Adjust as needed
    right=0.75in   % Adjust as needed
}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------

\begin{center}
    \textbf{\Huge \scshape Przemysław Chlipała} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/przennek}{\underline{github.com/przennek}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/przemys%C5%82aw-chlipa%C5%82a-712aa7106/}{\underline{linkedin}} $  $
    \faIcon{envelope}
    \href{mailto:przemyslaw.chlipala@gmail.com}
    {\underline{przemyslaw.chlipala@gmail.com}} $ $
    \faIcon{copyright}
    \href{https://www.coursera.org/user/2f79a023ccc47ab66ca3c0ca67fd77aa}{\underline{coursera}}
\end{center}

% -------------------- EDUCATION --------------------
% TODO REARANGE
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Jagiellonian University}{2017 - 2019}
      {M.S. Computer Science}{\href{https://github.com/przennek/neurons_activation_visualisation/blob/master/latex/praca.pdf}{Visualisation methods of artifical neurons' activation optimization.}}

    \resumeSubheading
      {AGH University}{2013 - 2017}
      {B.S. Applied Computer Science}{\href{https://misio.fis.agh.edu.pl/media/misiofiles/f697b33ada0bf415d95135a7010466a9.pdf}{A microservice application for managing tests.}}
      
  \resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{Akamai Technologies} $|$ \footnotesize\emph{Senior Software Engineer}\vspace{8pt}}{December 2020 -- June 2023}
          {\small{
            \begin{itemize}                
                \item \justifying Developed an IPSEC tunnels configuration service that generated and applied NETCONF-based configurations on the SRX. These tunnels were part of a larger solution that enabled mobile network users to access protected services without client-side VPN. Additionally, developed an SNMP-based monitoring service to track the status of IPSEC connections. Responsibilities included monitoring, testing, and implementing automated deployments. \\
                \textit{Key technologies: Java, Spring (MVC, data JPA, test, etc.), Docker, Kubernetes, Terraform, Microsoft Azure (queues, CosmosDB, Devops), JUnit5, Graphana, logzio.}

                \item Developed an authorization and authentication service called SPSON, used by mobile phones to access the secure DNS Server over DoH. Application covered REST API key-exchange services between on-premises DNS servers and a cloud-based SPSON, including APIs for token distribution and revocation to mobile devices. Implemented HMAC-based authorization for the authentication service, automated key rotation for over a million devices, conducted load testing, performance tuning, and implemented monitoring with alerting. Additionally, developed a frontend for operations (OPS). \\
                \textit{Key non proprietary technologies: Python, Flask, Docker, Cassandra, Bouncy Castle, locust, Graphana, vuejs, AWS (POC for partial migration out of an Akamai's cloud).}
            \end{itemize}
 
            }
          }
          
          \resumeProjectHeading
          {\textbf{Akamai Technologies} $|$ \footnotesize\emph{Software Engineer II}\vspace{8pt}}{May 2019 -- November 2020}
          {\small{
            \begin{itemize}
                \item \justifying
Development within a website access restriction application used for parental control. The application portal is responsible for loading and monitoring the status of modules used by the application. \\
                 \textit{Key technologies: Java, Spring, Hibernate, Docker, Kafka, PostgreSQL, AngularJS.}
                \item \justifying Developed a reactive web application for a campaign information pop-up utility used by the ISPs. \\ 
                \textit{Key technologies: Java, Spring (test, data JDBC), Docker, PostgreSQL.}
            \end{itemize}
            }
            }

          \resumeProjectHeading
          {\textbf{Akamai Technologies} $|$ \footnotesize\emph{Software Engineer}\vspace{8pt}}{June 2017 -- April 2019}
          {\small{
            \begin{itemize}
                \item \justifying Developed a managed content delivery network (MCDN) notification app that aggregated data from multiple sources and implemented logic to determine whether there were changes in the network configuration. \\
                \textit{Key non proprietary technologies: Spring, Mybatis, PostgreSQL, Docker }
            \end{itemize}
            }

          \resumeProjectHeading
          {\textbf{Sabre} $|$ \footnotesize\emph{Java Software Developer}\vspace{8pt}}{March 2017 -- May 2017}
          {\small{
          \begin{itemize}
              \item \justifying Rewriting an AutoSys jobs based application to a Spring based REST API. The application aimed to rebalance the contents of airline warehouses and provide detailed information on necessary stock adjustments.
          \end{itemize} 
}}

          \resumeProjectHeading
          {\textbf{Sabre} $|$ \footnotesize\emph{Software Engineer in tests associate}\vspace{8pt}}{October 2015 -- February 2017}
          {\small{
          \begin{itemize}
              \item \justifying Development of a test framework for automated end-to-end backend testing. Developed automated tests for the IX platform, including regression test automation and execution, as well as preparation of test case scenarios.
          \end{itemize}

}}

          \resumeProjectHeading
          {\textbf{Sabre} $|$ \footnotesize\emph{Intern}\vspace{8pt}}{July 2015 -- September 2015}
          {\small{
          \begin{itemize}
              \item \justifying Development of an E2E automated tests for the
Inteligence Exchange (IX) platform. Development of an application for a health check monitoring of said platform.
          \end{itemize}
}}

% TODO decide whether to keep it or to delete it
          \resumeProjectHeading
          {\textbf{Elbit Firma Innowacyjno – Wdrożeniowa} $|$ \footnotesize\emph{Intern}\vspace{8pt}}{July 2012 -- September 2012}
          {\small{
          \begin{itemize}
              \item   \justifying        Assistance with a water quality monitoring project. Development of
an embeded application for diagnostics of a speed measurement gate.
          \end{itemize}
}}

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
% TODO sprawdz i postaraj się wybrac kluczowe technologie ktorymi chcesz sie chwalic
% TODO wpisz że znasz angielski xD
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: Java, Python, SQL} \\
     
     \textbf{Tools}{: Git, Docker, Jenkins, Maven, Gradle, Sonar, Unix Shell, curl, Postman, Ansible, IntelliJ} \\
     
     \textbf{Frameworks}{: Spring, Flask} \\

     \textbf{Testing}{: JUnit, Spring Test, TestNG, Locust} \\
     
     \textbf{ORM}{: Spring Data, Hibernate, Mybatis} \\
     
     \textbf{DBs}{: PostgreSQL, CosmosDB, Cassandra} \\
     
     \textbf{Hands on experience}{: AWS, Azure, Kubernetes (k8s), Terraform, gevent, uWSGI, Vue }
     
    }}
 \end{itemize}

% -------------------- Lang --------------------
\section{Spoken languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Polish}{: native} \\
     \textbf{English}{: communicative} \\
    }}
 \end{itemize}

 % -------------------- Train --------------------
\section{Trainings}
  \resumeSubHeadingListStart
    \resumeSubSubheading
        {Kubernetes}{(Akamai/Chmurowisko) 2023}
    \resumeSubSubheading
        {Deep Learning}{(Coursera/deeplearning.ai) 2019}
    \resumeSubSubheading
        {Presentation skills advanced}{(Akamai) 2019}
    \resumeSubSubheading
        {Modern Business e-Correspondence}{(Akamai) 2018}
    \resumeSubSubheading
        {Stress management}{(Akamai) 2018}
    \resumeSubHeadingListEnd


\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Flow} $|$ \footnotesize\emph{C++, esp32}}{(Apricode) December 2023}
        \resumeItemListStart \justifying
            \resumeItem{Closed-source project emulating the capabilities of an automatic beer tap used by a popular pub network in Kraków.}
          \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Access-Control} $|$ \footnotesize\emph{Python, Flask, WebRTC, C++, esp32 + RPi, Vue.js, ansible, docker}}{July 2023 - October 2023}
        \resumeItemListStart \justifying
            \resumeItem{Intercom with an electric lock featuring custom-created electronic components, capable of conducting audio/video calls with Android clients. It offers the ability to apply time-based policies that control the duration the shared door remains open throughout the day. Project is open sourced, please find the sources on my github page.}
          \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Medwork} $|$ \footnotesize\emph{Typescript, Java, Spring, Angular 2}}{(Apricode) 2017}
        \resumeItemListStart \justifying
            \resumeItem{Closed source, web application for a medical center in Tuchów designed to facilitate occupational health care duties and invoicing.}
          \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{KW} $|$ \footnotesize\emph{Javascipt, Elasticsearch, Angular + electron}}{(Apricode) 2015}
        \resumeItemListStart \justifying
            \resumeItem{Electron application for the real estate developer's office in Poznań, designed for efficient querying of estate data.}
          \resumeItemListEnd
    

% RODO
\cfoot{\fontsize{9}{10}\selectfont \color{lightgray} I hereby give consent for my personal data included in my application to be processed for the purposes of the recruitment process.}

\end{document}
